\documentclass[11pt]{article}
\usepackage{graphicx} % Required for inserting images
\setlength{\parindent}{0pt}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage[utf8]{inputenc} 
\usepackage[T1]{fontenc}
\usepackage[brazil]{babel}
\usepackage{lipsum}
\usepackage[left=1.06cm,top=1.3cm,right=1.06cm,bottom=0.49cm]{geometry}




%by: Aline R. Antunes

\begin{document}
\begin{center}
    {\huge \textbf{John Jung}}\\ 
\end{center}

\begin{center}
    Temecula, California \textbullet \ johnhyukjung@gmail.com \textbullet \ (650) 868-8349 \\ 
    \hrulefill
\end{center}

% ------------- EXPERIENCE ---------------- %

\begin{center}
    \textbf{Experience}
\end{center}
\textbf{Tesla} \hfill Palo Alto, California

\textbf{Software Engineer Intern} \hfill January 2023 - September 2023
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Developed middleware services for end-system management tool used by InfraEng SRE teams.
    \item Shipped asset discovery feature for automated Prometheus metric onboarding/offboarding for IoT devices. 
    \item Improved PostGres based pub-sub system via job-state-based queue to reduce consumer callback time by 52\%.
    \item Wrote client socket APIs with Python/Go/Kong for enabling interaction between IoT devices and BI tools.
    \item Increased visibility of IoT devices by 96\% via creation of vendor specific Prometheus exporters in Python.
    \item Automated documentation system (NetBox) to live-update location, state, and network profile of power devices.
    \item \textit{Tech-stack: Kubernetes, Docker, Go, Python, PostGres, Redis, Kong, Prometheus}
\end{itemize}

\vspace{8pt}

\textbf{Tesla} \hfill Fremont, California

\textbf{Automation Engineering Intern} \hfill June 2022 - September 2022
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Configured CI/CD system for desktop automation and build testing using Jenkins, Ansible, and K8s.
    \item Implemented Github Actions pipeline for automated NetMiko and Selenium testing of 100+ applications.
    \item Undertook the migration of development and production environment to K8s to improve serviceability.
    \item \textit{Tech-stack: Jenkins, Kubernetes, Ansible, Python}
\end{itemize}

\vspace{8pt}

\textbf{Verdant Robotics} \hfill Hayward, California

\textbf{ML Operations Intern} \hfill June 2021 - September 2021 
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Wrote React web application for vision validation tool used by QA teams.
    \item Migrated TAO pipeline to Kubernetes based clusters to improve scalability.
    \item Developed WebGL based React module for displaying bounding boxes for image annotation.
    \item \textit{Tech-stack: Nvidia TAO SDK, C++, WebGL, React.js}
\end{itemize}

\vspace{8pt}

\textbf{AI Institute For Food Science}	\hfill Davis, CA

\textbf{Undergraduate Research Fellowship} \hfill September 2021 - December 2021
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Created GIS application for visualizing spoilage reports from tomato processing plants.
    \item Implemented ETL pipeline for live collecting spoilage reports.
    \item \textit{Tech-stack: React.js, ArcGIS, WebGL, Python, PostGres}
\end{itemize}

\vspace{8pt}

\textbf{aggieexplorer.com} \hfill Davis, CA

\textbf{Project Lead} \hfill January 2021 - June 2021
\begin{itemize}[noitemsep, topsep=0pt, partopsep=0pt, parsep=0pt]
    \item Lead team of 7 to build a React full-stack web application for university registrar system visualization.
    \item Gathered weekly team meetings for React tutorials and communication with university representative.
    \item \textit{Tech-stack: React.js, Python, MongoDB, AWS EC2}
\end{itemize}

% --------- SKILLS -----------

\begin{center}
    \textbf{Skills}
\end{center}

\textbf{Programming Languages}: \textit{C++, Python, JavaScript, Go}\\
\textbf{Frameworks}: \textit{React.js, ES6 OpenGL}\\
\textbf{Database Systems}: \textit{PostGres, MongoDB, Redis}\\
\textbf{Dev Tools}: \textit{Jenkins, Kubernetes (K8s), Docker, Kong}

% -------------- EDUCATION ---------------- %

\begin{center}
    \textbf{Education}
\end{center}
\textbf{University of California, Davis} \hfill Davis, California\\
Bachelor of Science in Computer Science, GPA: 3.6 \hfill June 2024\\
Relevant Coursework: Computer Architecture, Database Systems, Parallel Systems, Computer Graphics
\vspace{8pt}


\end{document}
